FraCaS: 80 percent complete

### 2019-02-26 paper2018/paper.tex
tiny compression attemps

\section{Background: GF, Monadic Dynamic Semantics, Coq}

\subsection{GF}
In GF, abstract syntax is comprised of: a) a number of syntactic
categories, and b) a number of syntactic construction functions. The latter
provide the means to compose basic syntactic categories into more complex
ones.  For example, consider the constructor: $AdjCN : AP → CN → CN$. This  expresses
that one can append an adjectival phrase to a common noun and obtain
a new common noun. Furthermore,  GF is equipped  with a library of mappings from abstract
syntax to the concrete s usyntax of varionatural languages. These mappings can be inverted by GF, thus offering
parsing from natural text into abstract syntax. However, in this project we skip the
parsing phase and use the parse trees constructed by \citet{Ljunglof:2012},
thereby avoiding any syntactic ambiguity. \todo{Do you want to further comment here?}

\subsection{Coq}
Coq is an interactive theorem prover (proof assistant) based on the
calculus of inductive constructions (CiC), i.e.  a lambda calculus
with dependent types. Coq is arguably one of the leading proof
assistants. It has famously been instrumental in formalising a proof
of the four-color theorem \citep{Gonthier:2008}, a proof of the odd
order theorem \citep{Gonthier:2013}, as well as developing CompCert, a
formally verified compiler for C \citep{Leroy}. Coq is a very powerful
reasoning engine that makes it fit for the task of NLI, when the
latter is formalized as theorem proving task. Its underlying higher
order logic is furthermore powerful enough to express fine-grained
logical semantics. Furthermore, Coq supports a number of constructions
that we will be using notably dependent typing and subtyping. These
features allow us to take care of specific NL phenomena
(e.g. subtyping is used in defining different adjectival inference
classes).

\subsection{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of
dealing with anaphora and ellipsis. There are a number of approaches
using monads or other equivalent constructions (e.g. continuations as in the work of
\citet{de2006}) for anaphora and ellipsis
\citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this
paper, we follow the approach described by
\citet{bernardy_jolli}. More details on this will be given in the next
section, where the actual system is presented.

>>>>

\section{Background: GF, Coq, Monadic Dynamic Semantics}

\paragraph{GF}
In GF, abstract syntax is comprised of: a) a number of syntactic
categories, and b) a number of syntactic construction functions. The latter
provide the means to compose basic syntactic categories into more complex
ones.  For example, consider the constructor: $AdjCN : AP → CN → CN$. This  expresses
that one can append an adjectival phrase to a common noun and obtain
a new common noun. Furthermore,  GF is equipped  with a library of mappings from abstract
syntax to the concrete s usyntax of varionatural languages. These mappings can be inverted by GF, thus offering
parsing from natural text into abstract syntax. However, in this project we skip the
parsing phase and use the parse trees constructed by \citet{Ljunglof:2012},
thereby avoiding any syntactic ambiguity. \todo{Do you want to further comment here?}

\paragraph{Coq}
Coq is an interactive theorem prover (proof assistant) based on the
calculus of inductive constructions (CiC), i.e.  a lambda calculus
with dependent types. Coq is arguably one of the leading proof
assistants. It has famously been instrumental in formalising a proof
of the four-color theorem \citep{Gonthier:2008}, a proof of the odd
order theorem \citep{Gonthier:2013}. Coq is a very powerful
reasoning engine that makes it fit for the task of NLI, when the
latter is formalized as theorem proving task. Its underlying higher
order logic is furthermore powerful enough to express fine-grained
logical semantics. Furthermore, Coq supports a number of constructions
that we will be using notably dependent typing and subtyping. These
features allow us to take care of specific NL phenomena
(e.g. subtyping is used in defining different adjectival inference
classes).

\paragraph{Dynamic Monadic Semantics}
Dynamic Monadic Semantics have been proven to be an effective way of
dealing with anaphora and ellipsis. There are a number of approaches
using monads or other equivalent constructions (e.g. continuations as in the work of
\citet{de2006}) for anaphora and ellipsis
\citet{Shan:2002,unger:2011,Barker:04,de2016,charlow:2017}. In this
paper, we follow the approach described by
\citet{bernardy_jolli}. More details on this will be given in the next
section, where the actual system is presented.
